### 2023-03-11 paper/content.tex
Updates from Overleaf

\begin{enumerate}
\item Calculate the \textit{total gradient amplitude} (TGA), also known as the
  3D analytic signal \citep{Roest1992Magnetic}, of the observed vertical
  component of the magnetic field. The TGA is entirely positive and tends to be
  more concentrated on top of the magnetic field sources than the observed
  magnetic field. The derivative calculation also acts as a high-pass filter,
  removing long-wavelength noise from the data.
\item Apply a contrast stretching method to re-scale the TGA to a new range
  defined by the lower and upper percentiles of the data in order to highlight
  the weaker signals, either coming from small or from deep-seated particles.
\item Use the Laplacian of Gaussian (LoG) method \citep{Kong2013} on the
  re-scaled TGA data to estimate the position and size of data windows
  containing the signal of each particle.
\end{enumerate}

@@

\begin{figure}[tb!]
  \centering
  \includegraphics[width=1\linewidth]{figures/simple-synthetic-data.png}
  \caption{
    Synthetic data and the various processing steps performed prior to the
    dipole moment inversion. 
    a) The synthetic noise-corrupted $b_z$ observations at 
    $z = \qty{5}{\micro\meter}$ due to four dipolar sources with different
    depths and dipole moment vectors 
    (see Table~\ref{tab_synthetic_simple_results}).
    b) The upward-continued data to $z = \qty{10}{\micro\meter}$ showing
    attenuated short-wavelength noise.
    c) The total gradient amplitude (TGA) calculated from the 
    upward-continued data, which is able to concentrate the signal on top
    of each dipolar source. 
    d) The contrast-stretched TGA, highlighting the signal of all four
    sources, including the weak central source.
    e) The detected source bounding boxes (black squares) which correctly
    identify the signal of all four sources.
    f) The estimated source locations (colored circles) from Euler 
    Deconvolution of the upward-continued data inside each bounding box. 
    The color represents the difference between the true and estimated 
    $z$ coordinates.
  }
  \label{fig_synthetic_simple_data}
\end{figure}

@@

Figure~\ref{complex-synthetic-stereograms} shows stereograms with the directions generated by the modeled (Fig.~\ref{complex-synthetic-stereograms}a) and the estimated vectors (Fig.~\ref{complex-synthetic-stereograms}b) for each sources. The distribution of the estimated directions are coincident with the true directions aside from a few sources, the same ones with the higher values of direction misfit (Fig.~\ref{complex-synthetic-comparison}a) which is probably associated with the mutual interference of sources close to each other or within the same window. When filtered to include only data with R\textsuperscript{2} \textgreater 0.95 and SNR \textgreater 10 the obtained direction distribution closer to the true distribution (Fig.~\ref{complex-synthetic-stereograms}c).

@@

After remanence acquisition, we performed a magnetic map with the Quantum
Diamond Microscope (QDM) at Harvard University over a sample section of
approximately 1410 $\mu$m x 2256 $\mu$m (Figure~\ref{W1GfysVYnX}a) with a grid
spacing of 2.35 $\mu$m and a sensor-sample distance of 5 $\mu$m, totaling
576x10\textsuperscript{3} data points. The QDM is housed in a shielded room, in
order to avoid the influence of the Earth's magnetic field \citep{Fu2020,
Glenn2017}. After applying the magnetic anomaly detection algorithm, it was
possible to determine the windows for 85 potential sources
(Figure~\ref{W1GfysVYnX}b).

\begin{figure}[tb]
\centering
\includegraphics[width=1\linewidth]{figures/RealData.png}
\caption{
a) Real sample data. b) Individual sources' window position (yellow squares)
obtained with the blob detection algorithm applied on the total gradient map.
}
\label{w1gfysvynx}
\end{figure}

After applying the ED algorithm, we performed the inversion of the magnetic
moment for each of the 85 windows selected previously. In order to reduce
considerably the computation time, the inversions were done within each data
window, instead of solving all sources parameters at the same time. We obtained
the magnetic moment (not shown) and the direction for all 85 magnetic grains
(Figure~\ref{NKOAMThaWA}a). Then, we calculated the residuals of the inversions
in each window and subsequently the coefficient of determination
R\textsuperscript{2}, which was used as a filter for the best directions
obtained. We used a cut-off limit of the coefficient of determination at 0.7
(Figure~\ref{NKOAMThaWA}b) EXPLICAR PORQUE USOU 0.7 AQUI E 0.95 NOS CASOS
SINTÉTICOS. This filtering technique removed unreliable responses showing more
clearly the expected directional clusters of hematite and magnetite crystals.
NÃO SABEMOS SE OS PONTOS RETIRADOS SÃO `UNRELIABLE RESPONSES'\dots ALÉM DISSO,
O FILTRO ELIMINA QUASE 50\% DAS FONTES IDENTIFICADAS, O QUE PODE SER UM
PROBLEMA SE TIVERMOS QUE APLICAR EM OUTROS CASOS REAIS. USAR O TESTE DE
NÃO-DIPOLARIDADE? TALVEZ SEJA MAIS INTERESSANTE, DADA A DISCUSSÃO QUE SEGUE.

\begin{figure}[tb]
\centering
\includegraphics[width=1\linewidth]{figures/RealDataStereo.png}
\caption{
a) The recovered data, without any type of filtering. b) Recovered data
filtered by the coefficient of determination ($R^ 2 \geq 0.7$), which shows
two clusters of direction located on each pole of the stereogram.
}
\label{nkoamthawa}
\end{figure}

@@

@@

We also present a new, faster, and cleaner way to solve the Euler equation in
determining the positioning of magnetic anomaly sources using a pre-selection
of magnetic anomaly source windows based on the Laplacian of the Gaussian
applied to total gradient anomaly maps. In this way, reducing the numerous
solutions to just one data window per source. After estimating the structural
index ($n = 3$) by approximating the sources generating the magnetic anomaly to
spheres/points, the Euler deconvolution is performed and the central position
of each source is determined.

@@

The test using a simple synthetic sample shows the great capability of the
method by retrieving not only the precise center positions, but also retrieving
the magnetization directions and intensity even under the considerable effect
of high-frequency noise (15 nT). While the complex synthetic sample data allows
observing the applicability of the method developed in real samples that are
more complex with varied magnetization directions and intensity, in addition to
also taking into account the high and low-frequency noise and sources with
variable sizes and depths.

The real sample data positively answered the question of the algorithm's
ability to deal with rocks thin-sections. But also, showed the acceptable
capacity (within the adequate R$^2$ threshold) of retrieving different
magnetization directions recorded by magnetic minerals with different
coercivities and magnetic signal disparities even greater than predicted in the
complex synthetic test.

>>>>

\begin{enumerate}
\item Calculate the \textit{total gradient amplitude} (TGA), also known as the 3D analytic signal \citep{Roest1992Magnetic}, of the observed vertical   component of the magnetic field. The TGA is entirely positive and tends to be more concentrated on top of the magnetic field sources than the observed magnetic field. The derivative calculation also acts as a high-pass filter, removing long-wavelength noise from the data.
\item Apply a contrast stretching method to re-scale the TGA to a new range   defined by the lower and upper percentiles of the data in order to highlight the weaker signals, either coming from small or from deep-seated particles.
%\item To enhance the quality of an image before the blob detection, we can also apply a common two-step approach that involves using a median filter and an unsharp mask filter \citep{VanderWalt2014}. The median filter reduces high-frequency noise (e.g., salt and pepper noise) in the image at the cost of smoothing slightly the edges, and the unsharp mask filter enhances the contrast and sharpness of edges. By applying a median filter followed by an unsharp mask filter, we can significantly improve the visual quality of an image while preserving the edges and the details.  
\item Use the Laplacian of Gaussian (LoG) method \citep{VanderWalt2014} on the   re-scaled TGA data to estimate the position and size of data windows containing the signal of each particle.
\end{enumerate}

@@

\begin{figure}[tb!]
  \centering
  \includegraphics[width=1\linewidth]{figures/simple-synthetic-data.png}
  \caption{
    Synthetic data and the various processing steps performed prior to the
    dipole moment inversion. 
    a) The synthetic noise-corrupted $b_z$ observations at 
    $z = \qty{5}{\micro\meter}$ due to four dipolar sources with different
    depths and dipole moment vectors 
    (see Table~\ref{tab_synthetic_simple_results}).
    b) The upward-continued data to $z = \qty{10}{\micro\meter}$ showing
    attenuated short-wavelength noise.
    c) The total gradient amplitude (TGA) calculated from the 
    upward-continued data, which is able to concentrate the signal on top
    of each dipolar source. 
    d) The contrast-stretched TGA, highlighting the signal of all four
    sources, including the weak central source.
    e) The detected source bounding boxes (black squares) that correctly
    identify the signal of all four sources.
    f) The estimated source locations (colored circles) from Euler 
    Deconvolution of the upward-continued data inside each bounding box. 
    The color represents the difference between the true and estimated 
    $z$ coordinates.
  }
  \label{fig_synthetic_simple_data}
\end{figure}

@@

Figure~\ref{complex-synthetic-stereograms} shows stereograms with the directions generated by the modeled (Fig.~\ref{complex-synthetic-stereograms}a) and the estimated vectors (Fig.~\ref{complex-synthetic-stereograms}b) for each source. The distribution of the estimated directions is coincident with the true directions aside from a few sources, the same ones with the higher values of direction misfit (Fig.~\ref{complex-synthetic-comparison}a) which is probably associated with the mutual interference of sources close to each other or within the same window. When filtered to include only data with R\textsuperscript{2} \textgreater 0.95 and SNR \textgreater 10 the obtained direction distribution is closer to the true distribution (Fig.~\ref{complex-synthetic-stereograms}c).

@@

After remanence acquisition, we performed a magnetic map with the Quantum
Diamond Microscope (QDM) at Harvard University over a sample section of
approximately 1410 $\mu$m x 2256 $\mu$m (Figure~\ref{real-data}a) with a grid
spacing of 2.35 $\mu$m and a sensor-sample distance of 5 $\mu$m, totaling
576x10\textsuperscript{3} data points. The QDM is housed in a shielded room, in
order to avoid the influence of the Earth's magnetic field \citep{Fu2020,
Glenn2017}. After applying the magnetic anomaly detection algorithm, it was
possible to determine the windows for 103 potential sources
(Figure~\ref{real-data}e).

\begin{figure}[tb]
\centering
\includegraphics[width=1\linewidth]{figures/real-data.png}
\caption{
a) Real sample data. b) Individual sources' window position (yellow squares)
obtained with the blob detection algorithm applied on the total gradient map.
}
\label{real-data}
\end{figure}

After applying the ED algorithm, we performed the inversion of the magnetic moment for each of the 103 windows selected previously. In order to reduce considerably the computation time, the inversions were done within each data window, instead of solving all sources parameters at the same time. We obtained the magnetic moment and the direction for all 103 magnetic grains (Figure~\ref{real-data-stereograms}a). Then, we calculated the residuals of the inversions in each window and subsequently the coefficient of determination R\textsuperscript{2} and signal-to-noise ratio (SNR), which were parameters used as filters for the best directions obtained. We considered a good fit to be achieved when $R^2$ was greater or equal to 0.85 and SNR was greater than to 10. An $R^2$ value of 0.85 indicates that 85\% of the measured magnetic data is explained by the predicted dipole model, which is equivalent as the non-dipolarity test approach \citep{Fu2020}. On the other hand, an SNR of 10 means that the dipolar signal is 10 times greater than the residual noise. By using these criteria, we ensured that the fit was sufficiently accurate and that the dipole model provided a reliable approximation of the original magnetic data. This filtering technique removed the poorly fit predicted models as well as the ones too corrupted with noise, showing more clearly the expected directional clusters of hematite and magnetite crystals (Figure~\ref{real-data-stereograms}b).

\begin{figure}[tb]
\centering
\includegraphics[width=1\linewidth]{figures/real-data-stereograms.png}
\caption{
a) The recovered data, without any type of filtering. b) Recovered data
filtered by the coefficient of determination ($R^ 2 \geq 0.7$), which shows
two clusters of direction located on each pole of the stereogram.
}
\label{real-data-stereograms}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Additional remarks}

While the windows approach violates the fundamental theory of the inversion problem that requires the sampled area to be finite and encapsulated by the inversion domain to ensure the uniqueness of results \citep{Baratchart2013,Lima2013}, our technique is similar to the one reported by \cite{Weiss2007}. The latter involves thresholding the long-distance interaction of each dipole in the SMM data, which excludes the effect of other dipoles by setting their contribution to zero, resulting in a sparse matrix that permits faster calculations. In contrast to this approach, we employ the windows technique and isolate the main signal of the desired dipole while excluding the rest from the inversion domain. This technique allows us to obtain an approximation of the dipole moment components of each source within a few seconds.

@@

We also present a new, faster, and cleaner way to solve the Euler equation in
determining the positioning of magnetic anomaly sources using a pre-selection
of magnetic anomaly source windows based on the Laplacian of the Gaussian
applied to total gradient anomaly maps. In this way, reducing the numerous
solutions to just one data window per source. After estimating the structural
index ($n = 3$) by approximating the sources generating the magnetic anomaly to
spheres/points, the Euler deconvolution is performed, and the central position
of each source is determined.

@@

The test using a simple synthetic sample shows the great capability of the method by retrieving not only the precise center positions, but also retrieving the magnetization directions and intensity even under the considerable effect of high-frequency noise (20 nT). While the complex synthetic sample data allows observing the applicability of the method developed in real samples that are more complex with varied magnetization directions and intensity, in addition to also taking into account the high and low-frequency noise and sources with variable sizes and depths.

\textbf{The real sample data positively answered the question of the algorithm's
ability to deal with rocks thin sections. But also, showed the acceptable
capacity (within the adequate R$^2$ threshold) of retrieving different
magnetization directions recorded by magnetic minerals with different
coercivities and magnetic signal disparities even greater than predicted in the
complex synthetic test.}

In our study, we assessed the quality of the fit between the predicted dipole model and the original magnetic data using two criteria: the coefficient of determination ($R^2$) and the signal-to-noise ratio (SNR).
